---
title: "single_ion_assay_table_curation"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load Packages
```{r}

library(readxl)
library(janitor)
library(tidyverse)

```

Read in sample table and make the column names R friendly with clean_names. 

We'll have to switch them back to the column names expected by ISA at the end
```{r}


s_OSD_508 <- read.delim("~/Desktop/OSD-508-ISA/s_GLDS-508 copy.txt")  %>% clean_names()


```

This workflow assumes you have already create the irradiation protocol itself, so the investigation file (i_investigation.txt) already reports the existence of a Protocol REF column for 'irradiation protocol'

Adding parameter: absorbed radiation dose, the associated units column and ontology columns.
```{r}

# Adding column based on other column. In this case 'factor_value_ionizing_radiation' is the existing column we are using as a key. The new parameters are the names after mutate()
s_OSD_508_copy <- s_OSD_508 %>%
  mutate(absorbed_radiation_dose = case_when(
    endsWith(factor_value_ionizing_radiation, "non-irradiated") ~ "",
    endsWith(factor_value_ionizing_radiation, "Cobalt-60 gamma radiation") ~ "100"
    ),.after = protocol_ref_1) %>% #You need to make sure this is the name of your column that contains 'irradiation protocol' or this code chunk will put your new parameters in the wrong place
    mutate(absorbed_radiation_dose_unit = case_when(
    endsWith(factor_value_ionizing_radiation, "non-irradiated") ~ "Not Applicable",
    endsWith(factor_value_ionizing_radiation, "Cobalt-60 gamma radiation") ~ "gray"
    ),.after = absorbed_radiation_dose) %>%
    mutate(absorbed_radiation_dose_unit_TSREF = case_when(
    endsWith(factor_value_ionizing_radiation, "non-irradiated") ~ "NCIT",
    endsWith(factor_value_ionizing_radiation, "Cobalt-60 gamma radiation") ~ "UO"
    ),.after = absorbed_radiation_dose_unit) %>%
    mutate(absorbed_radiation_dose_unit_TSACCESSION = case_when(
    endsWith(factor_value_ionizing_radiation, "non-irradiated") ~ "http://ncicb.nci.nih.gov/xml/owl/EVS/Thesaurus.owl#C48660",
    endsWith(factor_value_ionizing_radiation, "Cobalt-60 gamma radiation") ~ "http://purl.obolibrary.org/obo/UO_0000134"
    ), .after= absorbed_radiation_dose_unit_TSREF)


```



